### 2023-10-02 outputs/paper/paper.qmd
Upload the YAML and the introduction (first draft).

---
title: "My title"
author: "Yiliu Cao"
thanks: "Code and data from this analysis are available at: https://github.com/yiliuc/Bicycle_Thefts_2023.git"
date: "today"
date-format: "long"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| message: false
#| echo: false

#### Workspace set-up ####

## Load packages
library(tidyverse)
library(palmerpenguins)
library(here)

# read in the cleaned data
# setwd("/Users/caoyiliu/Desktop/U of T/Year 4/STA497/Bicycle_Thefts_2023")
cleaned_data <- read_csv(here("outputs/data/cleaned_data.csv"))
```

# Introduction

As the annual ranking by PeopleForBikes on 2022, Toronto has been named the 16th best major cycling city. In Toronto, there is about 300 kilometers on-street bike lanes and over 150 kilometers of off-street bike trails. Bicycle is becoming the main travel mode for the people living in Toronto. You can see people taking bicycle around each corner. However, as the number of bicycles increases each year, bicycles thefts had became a severe problem that needs to pay more attention on this. In Toronto, the bicycle thefts in Toronto surged during the past summer, nearly a 429 per cent increases. According to the neighborhood crime app by TPS, the downtown Toronto is place where the bicycle theft is mostly likely to occur, especially the U of T campus where the bicycle thefts is maximum.

Once the the bike is stolen, then the probability of getting it back is very low. However, even though the people lock their bikes, it may still be stolen as breaking the lock on the bicycle is a easy thing. You can even break the U lock with only a pen. Therefore, it is necessary for the bicycle riders to learn the feature influencing the possibility of bicycle to be stolen and estimate how likely their bicycle will be stolen. In this paper, I will use the historical bicycle thefts in Toronto to investigate the factors contributing to the bicycle thefts and tell the riders in what circumstances, the bicycle is most likely to be stolen.

In this paper, there will be four main parts: Data, Results, Discussion and Conclusion. In the Data section, I will introduce the data used in this paper and summarize the key variables. In addition to that, I will use the figures to show what kind of bicycles are most likely to be stolen as well as the places in the Results session. Moreover, in the Discussion session, I will emphasize the main findings and discuss how avoid the bicycle thefts. Finally, I will discuss the limitations and further conclude the entire paper in the Conclusion session.

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2023-10-02 outputs/paper/paper.qmd
Update the paper.qmd with Data session(first draft)

@@
 library(here)
+library(kableExtra)
 
@@
 cleaned_data <- read_csv(here("outputs/data/cleaned_data.csv"))
+raw_data <- read_csv(here("inputs/data/raw_bicycle_thefts_data.csv"))
 ```
@@
 # Data {#sec-data}
+The data will be used in this paper was obtained from Open Data Toronto Portal by the library `opendatatoronto`.
+The name of the data file is `Bicycle Thefts`.
+The data contains above 30,000 rows and about 30 columns.
+The raw data was cleaned using the open source statistical programming language with packages 1, 2, 3.
+In the cleaned data, it contains 11 variables which can be divided into three main categories.
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+## The Time of Bicycle Thefts Occurrence
+The cleaned data contains very detailed information regarding the occurrence time of each theft.
+The smallest unit is the occurrence hour of each theft.
+The table below shows the summary table for the occurrence of bicycle thefts
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+cleaned_data %>% 
+  group_by(occ_month) %>% 
+  summarise(n = n()) %>% 
+  arrange(desc(n)) %>% 
+  rename(`Occurrence Month` = occ_month,
+         `Count` = n) %>% 
+  kable()
 ```
 
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+## The Places Where the Bike was stolen
+The second main category in the cleaned data is describing the places of bicycle thefts.
+There are six main premises type of bicycle thefts, which are: Commercial, Apartment, Other, House, Educational, Transit and Other.
+The premises type here represent the places where the bicycle was stolen.
 
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("outputs/data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+cleaned_data %>% 
+  group_by(premises_type) %>% 
+  summarise(n = n()) %>% 
+  arrange(desc(n)) %>% 
+  rename(`Premise Type` = premises_type,
+         `Count` = n) %>% 
+  kable()
 ```
 
-Talk way more about it.
+## The Stolen Bicycles' Own Features
+The last category of variables in the cleaned data is the features of each stolen bicycle. The features of each stolen bike include its brand, type, color and cost.
 
-# Model
+```{r}
+cleaned_data %>% 
+  group_by(bike_type) %>% 
+  summarise(n = n()) %>% 
+  arrange(desc(n)) %>% 
+  rename(`Bike Type` = bike_type,
+         `Count` = n) %>% 
+  kable()
+```
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
+```{r}
+cleaned_data %>% 
+  group_by(bike_colour) %>% 
+  summarise(n = n()) %>% 
+  arrange(desc(n)) %>% 
+  rename(`Bike Colour` = bike_colour,
+         `Count` = n) %>% 
+  kable()
+```
 
@@
 
-Our results are summarized in @tbl-modelresults.
+## One
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
+## Two
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("outputs/models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
+## Three
 
@@
 
+# Conclusion
+
 ## Weaknesses and next steps
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2023-10-03 outputs/paper/paper.qmd
Update the three graphs (first draft)

@@
 cleaned_data %>% 
-  group_by(occ_month) %>% 
+  group_by(occ_year) %>% 
   summarise(n = n()) %>% 
   arrange(desc(n)) %>% 
-  rename(`Occurrence Month` = occ_month,
+  rename(`Occurrence Year` = occ_year,
          `Count` = n) %>% 
@@
 
-## One
+## There was a rebounace of bicycle thefts in 2022, especially for summer.
+```{r, echo = FALSE}
+# Ensure the cleaned_data dataframe has columns named 'Year', 'Month', and 'Bicycle_Thefts' or equivalent
 
-## Two
+# Summarize data by Year and Month
+summarized_data <- cleaned_data %>%
+  filter(occ_year %in% 2017:2022) %>%  # Filtering data for the years 2014 to 2022
+  group_by(occ_year, occ_month) %>%
+  summarize(Total_Thefts = n())  # Replace 'Bicycle_Thefts' with the correct column name if different
+
+# Plot the data
+summarized_data %>% 
+    mutate(occ_month = factor(occ_month, levels = month.name)) %>% 
+    ggplot(aes(x = occ_month, y = Total_Thefts, group = occ_year, color =  as.factor(occ_year))) +
+    geom_line(size = 1) +
+    scale_colour_manual(name = "Years", 
+                      values = c("grey", "black", "green", "red", "blue","skyblue")) +
+    labs(title = "The number of bicycle thefts from 2017 to 2022 by month",
+       x = "Month",
+       y = "Number of bicycle thefts") +
+    theme_minimal() +
+    guides(x = guide_axis(angle = 90))
+```
+
+Descriptions here
+
+## Increasing number of bicycle thefts on the outside and educational areas.
+```{r}
+cleaned_data <- cleaned_data %>% 
+  mutate(stolen_summer = case_when(occ_month %in% c("May", "June", "July", "August") ~ "Yes",
+                                   TRUE ~ "No"))
+cleaned_data |>
+  filter(occ_year >= 2020 & premises_type != "Other") %>% 
+  ggplot(mapping = aes(x = premises_type, fill=stolen_summer)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(
+    x = "Premises type",
+    y = "Number of thefts",
+    fill = "Stolen during summer?") +
+  facet_wrap(vars(occ_year)) +
+  guides(x = guide_axis(angle = 90)) +
+  theme(legend.position = "bottom")
+```
+
+Descriptions here
 
 ## Three
+
+```{r}
+mean_price <- mean(cleaned_data$bike_cost, na.rm = TRUE)
+top_colors <- cleaned_data %>%
+  count(bike_colour) %>%
+  arrange(desc(n)) %>%
+  slice(1:4) %>%
+  pull(bike_colour)
+top_bike_types <- cleaned_data %>%
+  count(bike_type) %>%
+  arrange(desc(n)) %>%
+  slice(1:6) %>%
+  pull(bike_type)
+
+cleaned_data <- cleaned_data %>%
+  mutate(above_mean = ifelse(bike_cost > mean_price, "Above Mean", "Below Mean"))
+
+cleaned_data %>%
+  filter(bike_colour %in% top_colors, bike_type %in% top_bike_types) %>%
+  mutate(bike_colour_new = case_when(bike_colour == "BLK" ~ "Black",
+                                     bike_colour == "BLU" ~ "Blue",
+                                     bike_colour == "GRY" ~ "Grey",
+                                     bike_colour == "WHI" ~ "White")) %>% 
+  ggplot(mapping = aes(x = bike_type, fill = above_mean)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x = "Bicycle Type",
+       y = "Number of Bicycle Thefts",
+       fill = "Price of Stolen Bicycles") +
+  facet_wrap(vars(bike_colour_new),
+             scales = "free") +
+  scale_fill_manual(values = c("Above Mean" = "#E69F00", "Below Mean" = "#204e4c")) +
+  guides(x = guide_axis(angle = 90)) +
+  theme(legend.position = "bottom")
+```
+
+Descriptions here
 

### 2023-10-03 outputs/paper/paper.qmd
Update the discussion session (first draft)

@@
 # Results
-
-## There was a rebounace of bicycle thefts in 2022, especially for summer.
+## Compare the bicycle thefts in the recent six years
 ```{r, echo = FALSE}
@@
 
-## Increasing number of bicycle thefts on the outside and educational areas.
+## Compare the premises types and probability to be stolen during summer.
 ```{r}
@@
 
-## Three
+## Compare the top 4 colours and top 5 bicycle types from bicycle thefts
 
@@
 
-## First discussion point {#sec-first-point}
+## Repeating patterns of bicycle thefts: expected to decrease in 2023.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+From Figure 1, it seems that the bicycle thefts happen most during the summer but less during the winter.
+According to Amanat, the number of bicycle thefts surged 429 per cent during the summer month.
+The potential reason behind this pattern is that people are more likely to ride bicycle during the summer but due to the cold weather, less people take bicycle during winter and hence the occurrence of bicycle thefts decreases.
 
-## Second discussion point
+For the summer month, we can observe a “pendulum movement“ in bicycle thefts.
+The number of thefts alternates annually, increasing one year and then decreasing the next.
+This trend repeats consistently from 2017 to 2022.
+Comparing 2022 to 2021, we see that the number of bicycle thefts during summer of 2022 started to increase again comparing to 2021.
+We may expect that the number of bicycle thefts decrease during the past summer.
+In addition, we can observe that most decrease is between 2020 and 2021, where there was about 200 decrease in the thefts during summer months.
+However, the potential reason behind this dramatic decrease is COVID, we can not use this to justify the number changed in bicycle thefts this year.
 
-## Third discussion point
+From 2017 to 2022, July is always the month with most bicycle thefts.
+Even though there will be an expected decrease in bicycle thefts in 2023 summer, the number of bicycle in July will still remain around 350, roughly 10 thefts per day.
+If you are a rider, then you really need to raise your awareness of bicycle thefts during July.
+
+## Increasing number of bicycle thefts on the outside and educational areas.
+From Figure 2, we can observe that the distribution of number of bicycle thefts in each year is roughly same.
+However, we can observe that apartment was the premise type that have highest bicycle thefts.
+However, thefts from the apartment decreases gradully from 2020 to 2023, instead, the number of bicycle thefts on streets, roads or highways (Outside) seems to increase gradually and dominated in 2022.
+In addition, the number of thefts in educational areas like school or university also increased.
+This suggest to students who take bicycle to school also need to protect their bicycle more.
+
+In addition, for all premises types in each year, we can observe that almost half was occurred during summer.
+Except for "Apartment", we can observe that the proportion of bikes that were stolen during summer increases.
+
+## No evidence indicates that the cheaper/more expensive bicycles are less/more likely to be stolen.
+From Figure 3, it seems that the black bikes is in favor of thieves.
+The amount of black bicycle lost is about the same as the other three colors combined.
+In terms of bicycle types, MT (mountain type) is bicycle type that is most likely to be stolen, followed by RG (Regular) which has almost same thefts with MT.
+
+In terms of price of bicycles, it seems that except EL, majority of stolen bicycles for the rest bicycle types have a price below the mean price.
+For the most two "welcome" bicycle types for thieves MT and RG, nearly eighty percent stolen bicycles for each color has a price lower than the mean price.
+This indicates that thieves will not evaluate the price of bicycles before they steal it.
+They pick a random bicycle to steal as long as the time is right.
 

### 2023-10-03 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -1,19 +1,66 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulate the bicycle thefts data
+# Author: Yiliu Cao
+# Date: 3 October 2023
+# Contact: yiliu.cao@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(knitr)
+library(kableExtra)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+set.seed(497)  
+num_samples <- 1000
 
+unique_occ_year <- c(2019, 2020, 2021, 2022)
+unique_occ_month <- c("December", "January", "November", "June", "February", 
+                      "March", "April", "October", "August", "September", "May", "July")  
+unique_premises_type <- c("BM", "EL", "FO", "MT", "OT", "RC")
+unique_bike_type <- c("Commercial", "Outside", "Apartment", "Other", "House", "Educational", "Transit")
+unique_bike_colour <- c("BLK", "WHI", "BLU", "GRY")
+min_bike_cost <- 100
+max_bike_cost <- 2000
+simulated_data <- data.frame(
+  occ_year = sample(unique_occ_year, num_samples, replace = TRUE),
+  occ_month = sample(unique_occ_month, num_samples, replace = TRUE),
+  premises_type = sample(unique_premises_type, num_samples, replace = TRUE),
+  bike_type = sample(unique_bike_type, num_samples, replace = TRUE),
+  bike_colour = sample(unique_bike_colour, num_samples, replace = TRUE),
+  bike_cost = round(runif(num_samples, min = min_bike_cost, max = max_bike_cost)), 0)
 
+# Create the summary table
+simulated_data %>% 
+  group_by(occ_year) %>% 
+  summarise(n = n()) %>% 
+  arrange(desc(n)) %>% 
+  rename(`Occurrence Year` = occ_year,
+         `Count` = n) %>% 
+  kable()
 
+simulated_data %>% 
+  group_by(premises_type) %>% 
+  summarise(n = n()) %>% 
[…]

### 2023-10-03 outputs/paper/paper.qmd
Update the abstract and conclusion (first draft)

@@
 date-format: "long"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study utilizes data on bicycle thefts sourced from the Toronto Open Data Portal.
+Preliminary findings indicate a increase propensity for bicycle thefts during summer months.
+While black mountain bicycles constitute a significant proportion of stolen bikes, it does not necessarily imply they are more susceptible to theft due to their overall prevalence.
+Moreover, the cost of a bicycle does not seem to influence its theft risk, thieves will not evaluate the price before they steal it.
+Future research should explore the role of neighborhoods as a potential factor influencing bicycle thefts."
 format: pdf
@@
 ```{r, echo = FALSE}
-# Ensure the cleaned_data dataframe has columns named 'Year', 'Month', and 'Bicycle_Thefts' or equivalent
+summarized_data <- cleaned_data %>%
+  filter(occ_year %in% 2017:2022) %>% 
+  group_by(occ_year, occ_month) %>%
+  summarize(Total_Thefts = n())
 
-# Summarize data by Year and Month
-summarized_data <- cleaned_data %>%
-  filter(occ_year %in% 2017:2022) %>%  # Filtering data for the years 2014 to 2022
-  group_by(occ_year, occ_month) %>%
-  summarize(Total_Thefts = n())  # Replace 'Bicycle_Thefts' with the correct column name if different
-
-# Plot the data
 summarized_data %>% 
@@
 ## Increasing number of bicycle thefts on the outside and educational areas.
+
 From Figure 2, we can observe that the distribution of number of bicycle thefts in each year is roughly same.
@@
 ## No evidence indicates that the cheaper/more expensive bicycles are less/more likely to be stolen.
+
 From Figure 3, it seems that the black bikes is in favor of thieves.
@@
 
-## Weaknesses and next steps
+This paper investigate the trends of bicycle thefts in Toronto in the perspectives of year trend, premises type and bikes' own features.
+By this paper, it shows that there was a rebounance of bicycle thefts in 2022 and it is expected that the occurrence of bicycle thefts in 2023 will decrease according to the historical data.
+In addition, the summer months are the months in a year that the bicycle thefts occurs most, nearly half bicycle thefts that are stolen during the summer.
+Moreover, the apartment such as condo and the outside areas such as streets or highways are the two most likely place to occur bicycle thefts.
+Besides, bicycle thefts is on the rise on the educational areas such as schools or universities have increase.
+Students should protect their bicycles.
 
-Weaknesses and next steps should also be included.
+In terms of bicycle own features.
+Even though one third of stolen bicycles are black, we can not say that black bicycles are more likely to be lost as number of black bicycles is high.
+However, one important trend is that the price of a bike will not influence its likelihood to be stolen.
+That said, a cheap and an expensive bike has the same probability to be stolen.
+Don’t take chances that your bike won’t be stolen even though it is cheap.
 
-\newpage
+However, this paper has limitations.
+The data for this paper comes from `opendatatoronto` which is not a up-to-date data.
+The data of bicycle thefts for 2023 is missing.
+This is crucial as we can verify the "pendulum movement" I discussed once we have the data of bicycle thefts in 2023.
+The second limitation is the lack of information of neighborhood for each bicycle theft.
+If we have the neighborhood information of bicycle thefts, then this paper will be more informative as it can tell the people living in the certain neighborhood to take more care of their bicycles.
+This will more helpful for them to avoid bicycle thefts.
+The last one is the accuracy of data.
+Some people may not report the bicycle thefts to the police.
+Instead, they only report to the insurance company to get money from the converage.
+In that case, the actual bicycle thefts may be even more and makes it hard to track the patterns.
+
+In the future study, instead of using data from open data toronto, using the data from toronto police service open protal or from the insurance companies regarding the bicycle thefts might be a better option.
+This will make the data more accurate and help us to find the true patterns of bicycle thefts in Toronto.
+In addition, the data from TPS contains the information of neighborhoods regarding the bicycle thefts.
+With the information of neighborhood, it can have better effects.
 

### 2023-10-03 outputs/paper/paper.qmd
Update the YAML for each chunk

@@
 library(kableExtra)
+library(knitr)
 
@@
 # Data {#sec-data}
+
 The data will be used in this paper was obtained from Open Data Toronto Portal by the library `opendatatoronto`.
@@
 ## The Time of Bicycle Thefts Occurrence
+
 The cleaned data contains very detailed information regarding the occurrence time of each theft.
@@
 ```{r}
+#| echo: false
+#| message: false
+#| label: tbl_theft_occ_year
+#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
 cleaned_data %>% 
@@
   summarise(n = n()) %>% 
-  arrange(desc(n)) %>% 
+  arrange(desc(occ_year)) %>% 
   rename(`Occurrence Year` = occ_year,
@@
 
-## The Places Where the Bike was stolen
+Table 1 shows the number of bicycle thefts from 2009 to 2022.
+The difference between 2009 to 2013 and 2014 to 2022 indicate the missing data for latter years.
+From 2014 to 2022, we can see that number of bicycle thefts increased first from 2014 to 2015, then the bicycle thefts droped gradually since 2018.
+The reported bicycle thefts for last year was about 2400.
+
+## The Premises Place Where the Bike was stolen
+
 The second main category in the cleaned data is describing the places of bicycle thefts.
@@
 ```{r}
+#| echo: false
+#| message: false
+#| label: a
+#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
 cleaned_data %>% 
@@
 
+Table 2 summarized the premises type of bicycle thefts.
+We can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention on their bicycle if they park it near the condo or on the street.
+
 ## The Stolen Bicycles' Own Features
+
 The last category of variables in the cleaned data is the features of each stolen bicycle. The features of each stolen bike include its brand, type, color and cost.
@@
 ```{r}
-cleaned_data %>% 
-  group_by(bike_type) %>% 
-  summarise(n = n()) %>% 
-  arrange(desc(n)) %>% 
-  rename(`Bike Type` = bike_type,
-         `Count` = n) %>% 
-  kable()
+#| echo: false
+#| message: false
+#| label: b
+#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
+summary_stats <- data.frame(
+  Mean = mean(cleaned_data$bike_cost, na.rm = TRUE),
+  SD = sd(cleaned_data$bike_cost, na.rm = TRUE),
+  Min = min(cleaned_data$bike_cost, na.rm = TRUE),
+  Median = median(cleaned_data$bike_cost, na.rm = TRUE),
+  Max = max(cleaned_data$bike_cost, na.rm = TRUE))
+
+kable(summary_stats)
+
 ```
 
+Table3 shows the bicycle price of stolen bicycles. The mean price of stolen bicycles is around 1000 dollars. However, it is surprising that the most expensive stolen bicycles worth 120,000 dollars.
+
 ```{r}
+#| echo: false
+#| message: false
+#| label: c
+#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
 cleaned_data %>% 
@@
 # Results
+
 ## Compare the bicycle thefts in the recent six years
-```{r, echo = FALSE}
+
+```{r}
+#| echo: false
+#| message: false
+#| label: d
+#| fig-cap: The number of bicycle thefts from 2017 to 2022 by month
 summarized_data <- cleaned_data %>%
@@
                       values = c("grey", "black", "green", "red", "blue","skyblue")) +
-    labs(title = "The number of bicycle thefts from 2017 to 2022 by month",
-       x = "Month",
+    labs(x = "Month",
          y = "Number of bicycle thefts") +
@@
 
-Descriptions here
+The Figure 1 compares the monthly bicycle thefts from 2017 to 2022 with each line with different colors representing different years.
+It seems that the summer has significant higher bicycle thefts than winter in each year.
+In addition, it seems that the July is the most severe month of bicycle thefts in each year, ranged from 350 to 550 from the previous years.
+On the beginning and ending of each year, the number of bicycle thefts were always stable, keeping constant around 100.
 
 ## Compare the premises types and probability to be stolen during summer.
+
 ```{r}
+#| echo: false
+#| message: false
+#| label: e
+#| fig-cap: Summary of Bicycle Thefts Occurrence Year
 cleaned_data <- cleaned_data %>% 
@@
     fill = "Stolen during summer?") +
+  scale_fill_manual(values = c("No" = "lightcoral", "Yes" = "lightgrey")) +
   facet_wrap(vars(occ_year)) +
@@
 
-Descriptions here
+Figure 3 compares the premises type of bicycle thefts in the recent three years and indicate the proportion of bicycles that are stolen during the summer.
+There are three facet indicating three different years.
+Each bar in each facet represent the number of bicycle thefts of a premises type.
+The filled color in each bar shows the proportion of bicycles that are stolen during the summer, with light coral meaning NO and light grey meaning Yes.
 
@@
 ```{r}
+#| echo: false
+#| message: false
+#| label: f
+#| fig-cap: Summary of Bicycle Thefts Occurrence Year
 mean_price <- mean(cleaned_data$bike_cost, na.rm = TRUE)
@@
 
-Descriptions here
+Figure 3 compares the number of bicycle thefts for the top 4 colours and top 5 bicycle types.
+Each bar represent the corresponding number of bicycles of a bike type under different colors.
+In addition, each bar is filled by two colors orange and dark teal representing the proportion of bicycles that have a price above mean or below mean price.
 
@@
 
-For the summer month, we can observe a “pendulum movement“ in bicycle thefts.
+For the summer month, we can observe a "pendulum movement" in bicycle thefts.
 The number of thefts alternates annually, increasing one year and then decreasing the next.
@@
 That said, a cheap and an expensive bike has the same probability to be stolen.
-Don’t take chances that your bike won’t be stolen even though it is cheap.
+Don't take chances that your bike won't be stolen even though it is cheap.
 

### 2023-10-03 outputs/paper/paper.qmd
Update the titles for each table and figure

@@
 ---
-title: "My title"
+title: "Assessing Bicycle Parking Safety in Toronto: The Multifaceted Nature of Theft Risk."
+title-block-banner: true
 author: "Yiliu Cao"
@@
 #| label: tbl_theft_occ_year
-#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
+#| tbl-cap: Summary of Bicycle Thefts Occurrence Year (2014 to 2022)
 cleaned_data %>% 
@@
   arrange(desc(occ_year)) %>% 
+  slice(1:9) %>% 
   rename(`Occurrence Year` = occ_year,
@@
 #| label: a
-#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
+#| tbl-cap: Summary of Bicycle Thefts In Terms of Premises Types
 cleaned_data %>% 
@@
 #| label: b
-#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
+#| tbl-cap: Summary of Stolen Bicycle Cost
 summary_stats <- data.frame(
@@
 #| echo: false
+#| include: false
 #| message: false
@@
   arrange(desc(n)) %>% 
+  slice(1:4) %>% 
   rename(`Bike Colour` = bike_colour,
@@
 #| label: d
-#| fig-cap: The number of bicycle thefts from 2017 to 2022 by month
+#| fig-cap: Number of bicycle thefts from 2017 to 2022 by month
 summarized_data <- cleaned_data %>%
@@
     ggplot(aes(x = occ_month, y = Total_Thefts, group = occ_year, color =  as.factor(occ_year))) +
-    geom_line(size = 1) +
+    geom_line(linewidth = 1) +
     scale_colour_manual(name = "Years", 
@@
 #| label: e
-#| fig-cap: Summary of Bicycle Thefts Occurrence Year
+#| fig-cap: Distribution of Bicycle Thefts by Premises Type and Seasonal Trends in Toronto
+
 cleaned_data <- cleaned_data %>% 
@@
 #| label: f
-#| fig-cap: Summary of Bicycle Thefts Occurrence Year
+#| fig-cap: Distribution of bicycle thefts for the Top 4 Colours and Top 5 Bicycle Types
+
 mean_price <- mean(cleaned_data$bike_cost, na.rm = TRUE)

### 2023-10-04 outputs/paper/paper.qmd
Update all the writing parts (second draft)

@@
 library(here)
-library(kableExtra)
 library(knitr)
+library(opendatatoronto)
 
@@
 
-As the annual ranking by PeopleForBikes on 2022, Toronto has been named the 16th best major cycling city.
-In Toronto, there is about 300 kilometers on-street bike lanes and over 150 kilometers of off-street bike trails.
-Bicycle is becoming the main travel mode for the people living in Toronto.
-You can see people taking bicycle around each corner.
-However, as the number of bicycles increases each year, bicycles thefts had became a severe problem that needs to pay more attention on this.
-In Toronto, the bicycle thefts in Toronto surged during the past summer, nearly a 429 per cent increases.
-According to the neighborhood crime app by TPS, the downtown Toronto is place where the bicycle theft is mostly likely to occur, especially the U of T campus where the bicycle thefts is maximum.
+In the 2022 annual rankings by PeopleForBikes [citation], Toronto has been named the 16th best cycling city in North America.
+Toronto has about 300 kilometers of on-street bike lanes and over 150 kilometers of off-street bike trails [citation].
+As traffic becomes heavier, cycling has become one of the primary transport modes for people living in Toronto.
+However, with more and more bicycles in the city, bicycle thefts have become a severe problem.
+That said, bicycle thefts in Toronto surged nearly 429 percent during the 2022 summer [citation].
+According to the neighborhood crime app by TPS [citation], bicycle theft is most likely to occur in downtown Toronto, especially the U of T campus, which is the hotspot of bicycle thefts.
 
-Once the the bike is stolen, then the probability of getting it back is very low.
-However, even though the people lock their bikes, it may still be stolen as breaking the lock on the bicycle is a easy thing.
-You can even break the U lock with only a pen.
-Therefore, it is necessary for the bicycle riders to learn the feature influencing the possibility of bicycle to be stolen and estimate how likely their bicycle will be stolen.
-In this paper, I will use the historical bicycle thefts in Toronto to investigate the factors contributing to the bicycle thefts and tell the riders in what circumstances, the bicycle is most likely to be stolen.
+Recovering a stolen bike is almost impossible [citation].
+Alarmingly, even though people lock their bikes, defeating a bike lock can be surprisingly simple.
+You can even break the U lock with only a pen [citation].
+Therefore, it will be necessary for cyclists to learn the factors increasing theft vulnerability and estimate the theft risk their bikes might have.
+In this paper, I will use the data on bicycle thefts in Toronto [citation] to investigate the factors contributing to bicycle thefts, aiming to unearth the determinants of such thefts and guide riders about high-risk scenarios.
 
-In this paper, there will be four main parts: Data, Results, Discussion and Conclusion.
-In the Data section, I will introduce the data used in this paper and summarize the key variables.
-In addition to that, I will use the figures to show what kind of bicycles are most likely to be stolen as well as the places in the Results session.
-Moreover, in the Discussion session, I will emphasize the main findings and discuss how avoid the bicycle thefts.
-Finally, I will discuss the limitations and further conclude the entire paper in the Conclusion session.
+There will be four main parts: Data, Results, Discussion, and Conclusion.
+The Data section will introduce the data used in this paper and highlight the key variables.
+In addition, there will be figures to visualize the factors contributing to bicycle thefts.
+Moreover, in the Discussion session, I will interpret the main findings using the previous tables and figures to discuss the potential advice for cyclists in Toronto.
+Finally, there will be further conclusions and limitations in the conclusion session.
 
-# Data {#sec-data}
+# Data
 
-The data will be used in this paper was obtained from Open Data Toronto Portal by the library `opendatatoronto`.
-The name of the data file is `Bicycle Thefts`.
-The data contains above 30,000 rows and about 30 columns.
-The raw data was cleaned using the open source statistical programming language with packages 1, 2, 3.
-In the cleaned data, it contains 11 variables which can be divided into three main categories.
+The data used in this paper was obtained from Open Data Toronto Portal by the library `opendatatoronto` [citation].
+The name of the data file is `Bicycle Thefts` [citation].
+The data contains more than 30,000 rows and about 30 columns.
+Data cleaning was executed using open-source statistical programming language `R` [citation] and R packages `tidyverse` [citation], `tidyr` [citation], and `janitor` [citation].
+The refined data set encompasses 11 distinct variables, which can be grouped into three primary categories.
 
-## The Time of Bicycle Thefts Occurrence
+## 1. The Time of Bicycle Thefts Occurrence
 
-The cleaned data contains very detailed information regarding the occurrence time of each theft.
-The smallest unit is the occurrence hour of each theft.
-The table below shows the summary table for the occurrence of bicycle thefts
+The cleaned data contains very detailed information regarding the occurrence time of each theft, detailing up to the specific hour of occurrence.
+The table below ([citation]) summarize the occurrence year of bicycle thefts.
 
@@
 Table 1 shows the number of bicycle thefts from 2009 to 2022.
-The difference between 2009 to 2013 and 2014 to 2022 indicate the missing data for latter years.
-From 2014 to 2022, we can see that number of bicycle thefts increased first from 2014 to 2015, then the bicycle thefts droped gradually since 2018.
-The reported bicycle thefts for last year was about 2400.
+Between 2014 and 2018, we can see that the number of bicycle thefts increased first, then the bicycle thefts dropped gradually since 2019.
+The reported number of bicycle thefts for last year was about 2400.
 
-## The Premises Place Where the Bike was stolen
+## 2. The Premises Place Where the Bike was stolen
 
-The second main category in the cleaned data is describing the places of bicycle thefts.
-There are six main premises type of bicycle thefts, which are: Commercial, Apartment, Other, House, Educational, Transit and Other.
-The premises type here represent the places where the bicycle was stolen.
+The second main category in the cleaned data is the premises type of each bicycle thefts.
+The premises type here represents the places where the bicycle was stolen.
+In this data, there are six main premises types of bicycle theft: Commercial, Apartment, Other, House, Educational, Transit, and Other.
+[citation] summarizes the number of thefts for each premises type.
 
@@
 #| message: false
-#| label: a
+#| label: tbl_theft_premises_type
 #| tbl-cap: Summary of Bicycle Thefts In Terms of Premises Types
+
 cleaned_data %>% 
@@
 ```
+From [citation], we can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention to their bicycles if they park them near the condo or on the street.
 
-Table 2 summarized the premises type of bicycle thefts.
-We can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention on their bicycle if they park it near the condo or on the street.
+## 3. The Stolen Bicycles' Features
 
-## The Stolen Bicycles' Own Features
-
-The last category of variables in the cleaned data is the features of each stolen bicycle. The features of each stolen bike include its brand, type, color and cost.
+The last category of variables in the cleaned data is the features of each stolen bicycle.
+The features of each stolen bike in this data include its brand, type, color, and cost.
+In this paper, I will focus more on its type, color and cost.
 
@@
 #| message: false
-#| label: b
+#| label: tbl_theft_bike_cost
 #| tbl-cap: Summary of Stolen Bicycle Cost
+
 summary_stats <- data.frame(
@@
 
-Table3 shows the bicycle price of stolen bicycles. The mean price of stolen bicycles is around 1000 dollars. However, it is surprising that the most expensive stolen bicycles worth 120,000 dollars.
-
-```{r}
-#| echo: false
-#| include: false
-#| message: false
-#| label: c
-#| tbl-cap: Summary of Bicycle Thefts Occurrence Year
-cleaned_data %>% 
-  group_by(bike_colour) %>% 
-  summarise(n = n()) %>% 
-  arrange(desc(n)) %>% 
-  slice(1:4) %>% 
-  rename(`Bike Colour` = bike_colour,
-         `Count` = n) %>% 
-  kable()
-```
+[citation] shows the bicycle price of stolen bicycles. The mean cost of stolen bikes is around 1000 dollars. However, it is surprising that the most expensive stolen bicycles is worth 120,000 dollars.
 
@@
 #| message: false
-#| label: d
+#| label: fig_year_trend
 #| fig-cap: Number of bicycle thefts from 2017 to 2022 by month
+
 summarized_data <- cleaned_data %>%
@@
 
-The Figure 1 compares the monthly bicycle thefts from 2017 to 2022 with each line with different colors representing different years.
-It seems that the summer has significant higher bicycle thefts than winter in each year.
-In addition, it seems that the July is the most severe month of bicycle thefts in each year, ranged from 350 to 550 from the previous years.
-On the beginning and ending of each year, the number of bicycle thefts were always stable, keeping constant around 100.
+[citation] compares the monthly bicycle thefts from 2017 to 2022, with each line with different colors representing different years.
+The summer seems to have significantly higher bicycle thefts than winter each year.
+In addition, July is the most severe month of bicycle thefts each year, ranging from 350 to 550 from the previous years.
+At the beginning and end of each year, bicycle thefts were always stable, keeping constant around 100.
 
@@
 #| message: false
-#| label: e
+#| label: fig_premises_type
 #| fig-cap: Distribution of Bicycle Thefts by Premises Type and Seasonal Trends in Toronto
@@
 
-Figure 3 compares the premises type of bicycle thefts in the recent three years and indicate the proportion of bicycles that are stolen during the summer.
-There are three facet indicating three different years.
-Each bar in each facet represent the number of bicycle thefts of a premises type.
-The filled color in each bar shows the proportion of bicycles that are stolen during the summer, with light coral meaning NO and light grey meaning Yes.
+Figure 3 compares the premises type of bicycle thefts in the recent three years and indicates the proportion of bicycles stolen during the summer.
+There are three facets marking three different years.
+Each bar in each facet represents the number of bicycle thefts of a premises type.
+The filled color in each bar shows the proportion of bicycles stolen during the summer, with light coral meaning NO and light grey meaning Yes.
 
-## Compare the top 4 colours and top 5 bicycle types from bicycle thefts
+## Compare the top 4 colors and top 5 bicycle types from bicycle thefts
 
@@
 #| message: false
-#| label: f
+#| label: fig_bike_type
 #| fig-cap: Distribution of bicycle thefts for the Top 4 Colours and Top 5 Bicycle Types
@@
 
-Figure 3 compares the number of bicycle thefts for the top 4 colours and top 5 bicycle types.
-Each bar represent the corresponding number of bicycles of a bike type under different colors.
-In addition, each bar is filled by two colors orange and dark teal representing the proportion of bicycles that have a price above mean or below mean price.
+Figure 3 compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types.
+Each bar represents the corresponding number of bicycles of a bike type under different colors.
+In addition, each bar is filled with two colors, orange and dark teal, representing the proportion of bicycles that have a price above the mean or below the mean price.
 
@@
 
-From Figure 1, it seems that the bicycle thefts happen most during the summer but less during the winter.
-According to Amanat, the number of bicycle thefts surged 429 per cent during the summer month.
-The potential reason behind this pattern is that people are more likely to ride bicycle during the summer but due to the cold weather, less people take bicycle during winter and hence the occurrence of bicycle thefts decreases.
+As illustrated in [citation], bicycle thefts peak during the summer months and dip in the winter.
+This seasonal trend aligns with Amanat's observation [citation] of a 429% surge in thefts during summertime.
+A plausible explanation for this fluctuation is the increased cycling activity in summer due to favorable weather.
+Conversely, the cold winter months deter many from cycling, resulting in fewer theft opportunities.
 
 For the summer month, we can observe a "pendulum movement" in bicycle thefts.
-The number of thefts alternates annually, increasing one year and then decreasing the next.
+The number of thefts oscillates annually, increasing one year and then decreasing the next.
 This trend repeats consistently from 2017 to 2022.
-Comparing 2022 to 2021, we see that the number of bicycle thefts during summer of 2022 started to increase again comparing to 2021.
+In addition, comparing 2022 to 2021, we see that the number of bicycle thefts during summer of 2022 started to increase again comparing to 2021.
 We may expect that the number of bicycle thefts decrease during the past summer.
-In addition, we can observe that most decrease is between 2020 and 2021, where there was about 200 decrease in the thefts during summer months.
-However, the potential reason behind this dramatic decrease is COVID, we can not use this to justify the number changed in bicycle thefts this year.
+Moreover, the most significant decrease is between 2020 and 2021, where there was about 200 decrease in the thefts during summer months.
+Although the COVID-19 pandemic might be a rationale for this substantial decline, it can not help us to predict the change of thefts for this year.
 
-From 2017 to 2022, July is always the month with most bicycle thefts.
-Even though there will be an expected decrease in bicycle thefts in 2023 summer, the number of bicycle in July will still remain around 350, roughly 10 thefts per day.
-If you are a rider, then you really need to raise your awareness of bicycle thefts during July.
+Throughout the six-year span, July consistently to be the highest number of thefts.
+Even if we project a downturn in thefts for summer 2023, the number of thefts in 2023 July are still anticipated to around 350 incidents, or nearly 10 thefts daily.
+For cyclists, this underscores the need for heightened vigilance in July.
 
@@
 
-From Figure 2, we can observe that the distribution of number of bicycle thefts in each year is roughly same.
-However, we can observe that apartment was the premise type that have highest bicycle thefts.
-However, thefts from the apartment decreases gradully from 2020 to 2023, instead, the number of bicycle thefts on streets, roads or highways (Outside) seems to increase gradually and dominated in 2022.
-In addition, the number of thefts in educational areas like school or university also increased.
-This suggest to students who take bicycle to school also need to protect their bicycle more.
+[citation] provides insights into the distribution of bicycle thefts over the years, which remains relatively consistent.
+Notably, apartments emerged as the predominant location for such thefts.
+Yet, there's a discernible decline in apartment-related thefts from 2020 to 2023.
+In contrast, thefts in open spaces like streets, roads, or highways (categorized as "Outside") have seen a gradual increase, becoming most prevalent in 2022.
+Educational premises, such as schools or universities, also witnessed an increase in theft incidents, underscoring the need for students to rasie caution when parking their bicycles on campus.
 
-In addition, for all premises types in each year, we can observe that almost half was occurred during summer.
-Except for "Apartment", we can observe that the proportion of bikes that were stolen during summer increases.
+For almost every premise type across all years, approximately half of the thefts occurred during summer.
+However, the number of bicycles stolen during summer increase gradually.
+This suggests that as the warmer months approach, bicycle owners should be particularly vigilant, regardless of where they park.
 
@@
 
-From Figure 3, it seems that the black bikes is in favor of thieves.
-The amount of black bicycle lost is about the same as the other three colors combined.
-In terms of bicycle types, MT (mountain type) is bicycle type that is most likely to be stolen, followed by RG (Regular) which has almost same thefts with MT.
+Figure 3 reveals a distinct preference among thieves for black bicycles.
+In fact, the number of stolen black bikes equals to the combined total of the next three colors.
+In terms of bicycle types, mountain bicycles (MT) is the theives' primary target, closely followed by regular (RG) bicycles, which experience nearly identical theft rates.
 
-In terms of price of bicycles, it seems that except EL, majority of stolen bicycles for the rest bicycle types have a price below the mean price.
-For the most two "welcome" bicycle types for thieves MT and RG, nearly eighty percent stolen bicycles for each color has a price lower than the mean price.
-This indicates that thieves will not evaluate the price of bicycles before they steal it.
-They pick a random bicycle to steal as long as the time is right.
+When it comes to price of bicycles, with the exception of the EL type, the majority of stolen bikes across other categories are priced below the mean.
+Specifically, for the most sought-after types by thieves, MT and RG.
+There were about eighty percent of the stolen bicycles  are priced below the mean.
+This suggests that thieves don't necessarily factor in the bicycle's value during their selection.
+Instead, they likely act on opportunity, choosing any bicycle that presents a convenient theft chance.
 
@@
 
-This paper investigate the trends of bicycle thefts in Toronto in the perspectives of year trend, premises type and bikes' own features.
-By this paper, it shows that there was a rebounance of bicycle thefts in 2022 and it is expected that the occurrence of bicycle thefts in 2023 will decrease according to the historical data.
-In addition, the summer months are the months in a year that the bicycle thefts occurs most, nearly half bicycle thefts that are stolen during the summer.
-Moreover, the apartment such as condo and the outside areas such as streets or highways are the two most likely place to occur bicycle thefts.
-Besides, bicycle thefts is on the rise on the educational areas such as schools or universities have increase.
-Students should protect their bicycles.
+This paper investigates the patterns of bicycle thefts in Toronto, discussing the annual trends, premises types, and characteristics of the stolen bicycles.
+The study found a resurgence in bicycle thefts in 2022, with forecasts suggesting a potential decline in 2023 based on historical data.
+A notable finding is the increased risk of bicycle thefts during summer months, which nearly half of all reported thefts happen during summer.
+Locations such as apartments and outdoor spaces like streets or highways are hotspots for these thefts.
+Alarmingly, educational institutions like schools and universities also see a rising trend in bicycle thefts, underscoring the need for heightened vigilance among student cyclists.
 
-In terms of bicycle own features.
-Even though one third of stolen bicycles are black, we can not say that black bicycles are more likely to be lost as number of black bicycles is high.
-However, one important trend is that the price of a bike will not influence its likelihood to be stolen.
-That said, a cheap and an expensive bike has the same probability to be stolen.
-Don't take chances that your bike won't be stolen even though it is cheap.
+In terms of the characteristics of stolen bicycles, this paper found that while a third of all thefts involve black bicycles, this does not equivalent to that black are more likely to be stolen due to the overall prevalence of black bicycles.
+Importantly, the study suggests that the price of a bicycle doesn't significantly alter its theft risk.
+Whether inexpensive or costly, all bicycles seem to be stolen equally.
 
 However, this paper has limitations.
-The data for this paper comes from `opendatatoronto` which is not a up-to-date data.
+The data for this paper comes from `opendatatoronto` [citation] which is not a up-to-date data.
 The data of bicycle thefts for 2023 is missing.
 This is crucial as we can verify the "pendulum movement" I discussed once we have the data of bicycle thefts in 2023.
-The second limitation is the lack of information of neighborhood for each bicycle theft.
-If we have the neighborhood information of bicycle thefts, then this paper will be more informative as it can tell the people living in the certain neighborhood to take more care of their bicycles.
-This will more helpful for them to avoid bicycle thefts.
-The last one is the accuracy of data.
-Some people may not report the bicycle thefts to the police.
-Instead, they only report to the insurance company to get money from the converage.
-In that case, the actual bicycle thefts may be even more and makes it hard to track the patterns.
+Secondly, the data set is lack of information of neighborhood for each bicycle theft which could have provided richer insights into high-risk areas, enabling more targeted preventive measures.
+Lastly, some people may not report the bicycle thefts to the police.
+Instead, they only report to the insurance company to get money from the coverage [citation].
+If that situation exists a lot, then our analyse will seriously underestimate the bicycle thefts in Toronto.
 
-In the future study, instead of using data from open data toronto, using the data from toronto police service open protal or from the insurance companies regarding the bicycle thefts might be a better option.
-This will make the data more accurate and help us to find the true patterns of bicycle thefts in Toronto.
-In addition, the data from TPS contains the information of neighborhoods regarding the bicycle thefts.
-With the information of neighborhood, it can have better effects.
+For the future study, instead of using data from open data Toronto, using the data from Toronto police service open portal or the insurance companies regarding the bicycle thefts might be a better option.
+Once we can have the information of neighborhoods of bicycle thefts, our analyses will be more nuanced and help the cyclists to make more effective preventive strategies.
 

### 2023-10-04 scripts/02-data_cleaning.R
Update 02-data_cleaning.R

@@ -8,6 +8,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(tidyr)
+library(janitor)
 
 #### Clean data ####
 raw_data <- read_csv("inputs/data/raw_bicycle_thefts_data.csv")
@@ -25,8 +27,8 @@ cleaned_data <-
          BIKE_TYPE,
          BIKE_COLOUR,
          BIKE_COST) |>
-  tidyr::drop_na() |>
-  janitor::clean_names()
+  drop_na() |>
+  clean_names()
 
 #### Save data ####
 write_csv(x = cleaned_data, file = "outputs/data/cleaned_data.csv")

### 2023-10-04 outputs/paper/paper.qmd
Update the in-tex citations
Citations for tables and figures are not fixed

@@
 
-In the 2022 annual rankings by PeopleForBikes [citation], Toronto has been named the 16th best cycling city in North America.
-Toronto has about 300 kilometers of on-street bike lanes and over 150 kilometers of off-street bike trails [citation].
+In the 2022 annual rankings by PeopleForBikes [@silvestre2022], Toronto has been named the 16th best cycling city in North America.
+Toronto has about 300 kilometers of on-street bike lanes and over 150 kilometers of off-street bike trails [@jen2023].
 As traffic becomes heavier, cycling has become one of the primary transport modes for people living in Toronto.
 However, with more and more bicycles in the city, bicycle thefts have become a severe problem.
-That said, bicycle thefts in Toronto surged nearly 429 percent during the 2022 summer [citation].
-According to the neighborhood crime app by TPS [citation], bicycle theft is most likely to occur in downtown Toronto, especially the U of T campus, which is the hotspot of bicycle thefts.
+That said, bicycle thefts in Toronto surged nearly 429 percent during the 2022 summer [@amanat2023].
+According to the neighborhood crime app by TPS [@torontopolice_nodate], bicycle theft is most likely to occur in downtown Toronto, especially the U of T campus, which is the hotspot of bicycle thefts.
 
-Recovering a stolen bike is almost impossible [citation].
+Recovering a stolen bike is almost impossible [@rider2021].
 Alarmingly, even though people lock their bikes, defeating a bike lock can be surprisingly simple.
-You can even break the U lock with only a pen [citation].
+You can even break the U lock with only a pen [@wikihow2022].
 Therefore, it will be necessary for cyclists to learn the factors increasing theft vulnerability and estimate the theft risk their bikes might have.
-In this paper, I will use the data on bicycle thefts in Toronto [citation] to investigate the factors contributing to bicycle thefts, aiming to unearth the determinants of such thefts and guide riders about high-risk scenarios.
+In this paper, I will use the data on bicycle thefts in Toronto [@bicyclethefts] to investigate the factors contributing to bicycle thefts, aiming to unearth the determinants of such thefts and guide riders about high-risk scenarios.
 
@@
 
-The data used in this paper was obtained from Open Data Toronto Portal by the library `opendatatoronto` [citation].
-The name of the data file is `Bicycle Thefts` [citation].
+The data used in this paper was obtained from Open Data Toronto Portal by the library `opendatatoronto` [@opendatatoronto].
+The name of the data file is `Bicycle Thefts` [@bicyclethefts].
 The data contains more than 30,000 rows and about 30 columns.
-Data cleaning was executed using open-source statistical programming language `R` [citation] and R packages `tidyverse` [citation], `tidyr` [citation], and `janitor` [citation].
+Data cleaning was executed using open-source statistical programming language `R` [@citeR] and R packages `tidyverse` [@tidyverse], `tidyr` [@tidyr], and `janitor` [@janitor].
 The refined data set encompasses 11 distinct variables, which can be grouped into three primary categories.
@@
 The cleaned data contains very detailed information regarding the occurrence time of each theft, detailing up to the specific hour of occurrence.
-The table below ([citation]) summarize the occurrence year of bicycle thefts.
+The table below @tbl_theft_occ_year summarize the occurrence year of bicycle thefts.
 
@@
          `Count` = n) %>% 
-  kable()
+  kable(booktabs = TRUE)
 ```
 
-Table 1 shows the number of bicycle thefts from 2009 to 2022.
+@tbl_theft_occ_year shows the number of bicycle thefts from 2009 to 2022.
 Between 2014 and 2018, we can see that the number of bicycle thefts increased first, then the bicycle thefts dropped gradually since 2019.
@@
 In this data, there are six main premises types of bicycle theft: Commercial, Apartment, Other, House, Educational, Transit, and Other.
-[citation] summarizes the number of thefts for each premises type.
+[@tbl_theft_premises_type] summarizes the number of thefts for each premises type.
 
@@
 ```
-From [citation], we can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention to their bicycles if they park them near the condo or on the street.
+
+From @tbl_theft_premises_type, we can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention to their bicycles if they park them near the condo or on the street.
 
@@
 
-[citation] shows the bicycle price of stolen bicycles. The mean cost of stolen bikes is around 1000 dollars. However, it is surprising that the most expensive stolen bicycles is worth 120,000 dollars.
+@tbl_theft_bike_cost shows the bicycle price of stolen bicycles.
+The mean cost of stolen bikes is around 1000 dollars.
+However, it is surprising that the most expensive stolen bicycles is worth 120,000 dollars.
 
@@
 
-[citation] compares the monthly bicycle thefts from 2017 to 2022, with each line with different colors representing different years.
+@fig_year_trend compares the monthly bicycle thefts from 2017 to 2022, with each line with different colors representing different years.
 The summer seems to have significantly higher bicycle thefts than winter each year.
@@
 
-Figure 3 compares the premises type of bicycle thefts in the recent three years and indicates the proportion of bicycles stolen during the summer.
+@fig_premises_type compares the premises type of bicycle thefts in the recent three years and indicates the proportion of bicycles stolen during the summer.
 There are three facets marking three different years.
@@
 
-Figure 3 compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types.
+@fig_bike_type compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types.
 Each bar represents the corresponding number of bicycles of a bike type under different colors.
@@
 
-As illustrated in [citation], bicycle thefts peak during the summer months and dip in the winter.
-This seasonal trend aligns with Amanat's observation [citation] of a 429% surge in thefts during summertime.
+As illustrated in @fig_year_trend, bicycle thefts peak during the summer months and dip in the winter.
+This seasonal trend aligns with Amanat's observation [@amanat2023] of a 429% surge in thefts during summertime.
 A plausible explanation for this fluctuation is the increased cycling activity in summer due to favorable weather.
@@
 
-[citation] provides insights into the distribution of bicycle thefts over the years, which remains relatively consistent.
+@fig_premises_type provides insights into the distribution of bicycle thefts over the years, which remains relatively consistent.
 Notably, apartments emerged as the predominant location for such thefts.
@@
 
-Figure 3 reveals a distinct preference among thieves for black bicycles.
+@fig_bike_type reveals a distinct preference among thieves for black bicycles.
 In fact, the number of stolen black bikes equals to the combined total of the next three colors.
@@
 However, this paper has limitations.
-The data for this paper comes from `opendatatoronto` [citation] which is not a up-to-date data.
+The data for this paper comes from `opendatatoronto` [@opendatatoronto]] which is not a up-to-date data.
 The data of bicycle thefts for 2023 is missing.
@@
 Lastly, some people may not report the bicycle thefts to the police.
-Instead, they only report to the insurance company to get money from the coverage [citation].
+Instead, they only report to the insurance company to get money from the coverage \[citation\].
 If that situation exists a lot, then our analyse will seriously underestimate the bicycle thefts in Toronto.

### 2023-10-04 outputs/paper/paper.qmd
Update the in-text citation
Fix the citation errors for tables and figures.

@@
 
-## 1. The Time of Bicycle Thefts Occurrence
+## The Time of Bicycle Thefts Occurrence
 
 The cleaned data contains very detailed information regarding the occurrence time of each theft, detailing up to the specific hour of occurrence.
-The table below @tbl_theft_occ_year summarize the occurrence year of bicycle thefts.
+The table below @tbl-theft-occ-year summarize the occurrence year of bicycle thefts.
 
@@
 #| message: false
-#| label: tbl_theft_occ_year
+#| label: tbl-theft-occ-year
 #| tbl-cap: Summary of Bicycle Thefts Occurrence Year (2014 to 2022)
@@
 
-@tbl_theft_occ_year shows the number of bicycle thefts from 2009 to 2022.
+@tbl-theft-occ-year shows the number of bicycle thefts from 2009 to 2022.
 Between 2014 and 2018, we can see that the number of bicycle thefts increased first, then the bicycle thefts dropped gradually since 2019.
@@
 
-## 2. The Premises Place Where the Bike was stolen
+## The Premises Place Where the Bike was stolen
 
@@
 In this data, there are six main premises types of bicycle theft: Commercial, Apartment, Other, House, Educational, Transit, and Other.
-[@tbl_theft_premises_type] summarizes the number of thefts for each premises type.
+@tbl-theft-premises-type summarizes the number of thefts for each premises type.
 
@@
 #| message: false
-#| label: tbl_theft_premises_type
+#| label: tbl-theft-premises-type
 #| tbl-cap: Summary of Bicycle Thefts In Terms of Premises Types
@@
 
-From @tbl_theft_premises_type, we can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention to their bicycles if they park them near the condo or on the street.
+From @tbl-theft-premises-type, we can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention to their bicycles if they park them near the condo or on the street.
 
-## 3. The Stolen Bicycles' Features
+## The Stolen Bicycles' Features
 
@@
 #| message: false
-#| label: tbl_theft_bike_cost
+#| label: tbl-theft-bike-cost
 #| tbl-cap: Summary of Stolen Bicycle Cost
@@
 
-@tbl_theft_bike_cost shows the bicycle price of stolen bicycles.
+@tbl-theft-bike-cost shows the bicycle price of stolen bicycles.
 The mean cost of stolen bikes is around 1000 dollars.
@@
 #| message: false
-#| label: fig_year_trend
+#| label: fig-year-trend
 #| fig-cap: Number of bicycle thefts from 2017 to 2022 by month
@@
 
-@fig_year_trend compares the monthly bicycle thefts from 2017 to 2022, with each line with different colors representing different years.
+@fig-year-trend compares the monthly bicycle thefts from 2017 to 2022, with each line with different colors representing different years.
 The summer seems to have significantly higher bicycle thefts than winter each year.
@@
 #| message: false
-#| label: fig_premises_type
+#| label: fig-premises-type
 #| fig-cap: Distribution of Bicycle Thefts by Premises Type and Seasonal Trends in Toronto
@@
 
-@fig_premises_type compares the premises type of bicycle thefts in the recent three years and indicates the proportion of bicycles stolen during the summer.
+@fig-premises-type compares the premises type of bicycle thefts in the recent three years and indicates the proportion of bicycles stolen during the summer.
 There are three facets marking three different years.
@@
 #| message: false
-#| label: fig_bike_type
+#| label: fig-bike-type
 #| fig-cap: Distribution of bicycle thefts for the Top 4 Colours and Top 5 Bicycle Types
@@
 
-@fig_bike_type compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types.
+@fig-bike-type compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types.
 Each bar represents the corresponding number of bicycles of a bike type under different colors.
@@
 
-As illustrated in @fig_year_trend, bicycle thefts peak during the summer months and dip in the winter.
+As illustrated in @fig-year-trend, bicycle thefts peak during the summer months and dip in the winter.
 This seasonal trend aligns with Amanat's observation [@amanat2023] of a 429% surge in thefts during summertime.
@@
 
-@fig_premises_type provides insights into the distribution of bicycle thefts over the years, which remains relatively consistent.
+@fig-premises-type provides insights into the distribution of bicycle thefts over the years, which remains relatively consistent.
 Notably, apartments emerged as the predominant location for such thefts.
@@
 
-@fig_bike_type reveals a distinct preference among thieves for black bicycles.
+@fig-bike-type reveals a distinct preference among thieves for black bicycles.
 In fact, the number of stolen black bikes equals to the combined total of the next three colors.

### 2023-10-04 outputs/paper/paper.qmd
Update the comments and styles

@@
 #### Workspace set-up ####
-
 ## Load packages
@@
 # read in the cleaned data
-# setwd("/Users/caoyiliu/Desktop/U of T/Year 4/STA497/Bicycle_Thefts_2023")
 cleaned_data <- read_csv(here("outputs/data/cleaned_data.csv"))
-raw_data <- read_csv(here("inputs/data/raw_bicycle_thefts_data.csv"))
 ```
@@
 #| tbl-cap: Summary of Bicycle Thefts Occurrence Year (2014 to 2022)
+
+# Create the table for the occ_year
 cleaned_data %>% 
@@
 
+# Create the table for premises_type
 cleaned_data %>% 
@@
 
+# Create the table for bike_cost
 summary_stats <- data.frame(
@@
 kable(summary_stats)
-
 ```
@@
 
+# Filter the data from cleaned_data which contains only the bicycle thefts
+# from 2017 to 2022 and calculate the total number of thefts in each month
+# and year
 summarized_data <- cleaned_data %>%
@@
 
+# Use the summarized data to draw the graph showing the yearly trend in 
+# bicycle thefts by month
 summarized_data %>% 
@@
 
+# Create the graph showing the number of thefts under different premises type in
+# the recent three years.
 cleaned_data <- cleaned_data %>% 
+  # Mutate the occ_month so that they are be arranged in order
   mutate(stolen_summer = case_when(occ_month %in% c("May", "June", "July", "August") ~ "Yes",
@@
 
-## Compare the top 4 colors and top 5 bicycle types from bicycle thefts
+## Compare the top 4 colors and top 6 bicycle types from bicycle thefts
 
@@
 #| label: fig-bike-type
-#| fig-cap: Distribution of bicycle thefts for the Top 4 Colours and Top 5 Bicycle Types
+#| fig-cap: Distribution of bicycle thefts for the Top 4 Colours and Top 6 Bicycle Types
+
+# Compare the the top 4 colors and top 6 bicycle types in bicycle thefts
+# Also find the proportion of bikes that is under mean price
 
 mean_price <- mean(cleaned_data$bike_cost, na.rm = TRUE)
+
+# Find the top 4 colors
 top_colors <- cleaned_data %>%
@@
   pull(bike_colour)
+
+# Find the top 6 stolen bicycle types
 top_bike_types <- cleaned_data %>%
@@
 
+# Create a new column indicate the price of each stolen bicycle relative to mean
 cleaned_data <- cleaned_data %>%
@@
 
+# Then plot the graph
 cleaned_data %>%
@@
 
-@fig-bike-type compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types.
+@fig-bike-type compares the number of bicycle thefts for the top 4 colors and top 6 bicycle types.
 Each bar represents the corresponding number of bicycles of a bike type under different colors.

### 2023-10-04 scripts/01-download_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from toronto open data portal
+# Purpose: Downloads and saves the data from Toronto open data portal
 # Author: Yiliu Cao
 # Date: 1 October 2023
 # Contact: yiliu.cao@mail.utoronto.ca

### 2023-12-19 outputs/paper/paper.qmd
Update the final paper

@@
 ---
-title: "Assessing Bicycle Parking Safety in Toronto: The Multifaceted Nature of Theft Risk."
+title: "Analyzing Bicycle Parking Safety in Toronto: The Multifaceted Nature of Theft Risk"
 title-block-banner: true
@@
 thanks: "Code and data from this analysis are available at: https://github.com/yiliuc/Bicycle_Thefts_2023.git"
-date: "today"
+date: "2023-10-4"
 date-format: "long"
